Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-06 paper.tex
Predictors and transformers

The estimator interface also defines a \texttt{fit} method. Invoking this method
causes the estimator to learn from a training set (e.g., supplied as two arrays
\texttt{X} and \texttt{y} in supervised learning estimators). Its task, from an
API point of view, is to run a learning algorithm and to determine model-
specific parameters from the training data and set these as attributes on the
estimator object.

As an example, let us consider a supervised learning task using linear regression.
Given the API defined above, solving this problem is as simple as:
\begin{center}
\texttt{clf = LinearRegression(penalty="l1").fit(X, y)}
\end{center}
In this snippet, a \texttt{LinearRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence enabling $L1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the arrays \texttt{X} and
\texttt{y}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LinearRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}. Let us also note the snippet relies on the
fact that the \texttt{fit} method always returns the object it was called
on\footnote{I.e., the \texttt{self} argument it was called on.}, hence making
method chaining  possible.

In \textit{scikit-learn}, classical learning algorithms are not the only objects
to be implemented as estimators. For example, preprocessing routines (e.g.,
vectorization of text documents, scaling of attributes, etc) or feature
extraction techniques also implement the same interface. Even those estimators
that are entirely stateless and therefore do not require the \texttt{fit} method
to perform any useful work implement the estimator interface. As we will
illustrate in the next section, this design pattern is indeed of prime
importance for consistency, composition and parameter validation reasons.

\textbf{Predictors.}

\textbf{Transformers.}

\vspace{3cm}

@@

Importantly, the parameters learned by an estimator
are exposed as \textit{public} attributes on the trained object.
This facilitates model inspection
and makes it possible to train a model using scikit-learn,
export it to a (standardized or custom) external data format
and use the learned parameters in a different piece of code,
perhaps a prediction algorithm implemented in a different language
or one that combines the model parameters with other information
to build a custom model.
% XXX Hard to follow phrasing below
Of course, it also forces the developers to think carefully
about what might, in a more ``black box''-style toolkit,
be considered the internals of objects,
since authors of client code are allowed to rely
on the names and formats of model parameters.

>>>>

The estimator interface also defines a \texttt{fit} method. Invoking this method
causes the estimator to learn from a training set (e.g., supplied as two arrays
\texttt{X} and \texttt{y} in supervised learning estimators). Its task, from an
API point of view, is to run a learning algorithm and to determine model-
specific  parameters from the training data and set these as attributes on the
estimator object. As a convention, the parameters learned by an estimator are
exposed as public attributes\footnote{Note that the learned parameters are
different from the hyper-parameters given to the constructor. To distinguish
between the two, learned parameters are all suffixed with a trailing underscore
(e.g., \texttt{clf.coef\_} in the case of linear models is the vector of
coefficients learned from the data).} on the trained object.

% Importantly, the parameters learned by an estimator
% are exposed as \textit{public} attributes on the trained object.
% This facilitates model inspection
% and makes it possible to train a model using scikit-learn,
% export it to a (standardized or custom) external data format
% and use the learned parameters in a different piece of code,
% perhaps a prediction algorithm implemented in a different language
% or one that combines the model parameters with other information
% to build a custom model.
% % XXX Hard to follow phrasing below
% Of course, it also forces the developers to think carefully
% about what might, in a more ``black box''-style toolkit,
% be considered the internals of objects,
% since authors of client code are allowed to rely
% on the names and formats of model parameters.

As an example, let us consider a supervised learning task using linear regression.
Given the API defined above, solving this problem is as simple as:
\begin{center}
\texttt{clf = LinearRegression(penalty="l1").fit(X, y)}
\end{center}
In this snippet, a \texttt{LinearRegression} estimator is first initialized by
setting the \texttt{penalty} hyper-parameter to \texttt{l1}, hence enabling $L1$
regularization, and using default values for all other hyper-parameters. Upon
\texttt{fit}, the model is then learned from the arrays \texttt{X} and
\texttt{y}. Also, since all estimators share the same interface, using a
different learning algorithm is as simple as replacing the constructor. For
example, to build a Random Forest on the same training data, one would simply
have to replace \texttt{LinearRegression(penalty="l1")} in the snippet above by
\texttt{RandomForestClassifier()}. Let us also note that the snippet relies on the
fact that the \texttt{fit} method always returns the object it was called
on\footnote{I.e., the \texttt{self} argument it was called on.}, hence making
method chaining  possible.

In \textit{scikit-learn}, classical learning algorithms are not the only objects
to be implemented as estimators. For example, preprocessing routines (e.g.,
vectorization of text documents, scaling of attributes, etc) or feature
extraction techniques also implement the same interface. Even those estimators
that are entirely stateless and therefore do not require the \texttt{fit} method
to perform any useful work implement the estimator interface. As we will
illustrate in the next sections, this design pattern is indeed of prime
importance for consistency, composition and parameter validation reasons.

\textbf{Predictors.} The \textit{predictor} interface defines a \texttt{predict}
method taking as input some dataset \texttt{X} and producing as output
predictions for \texttt{X} based on the learned parameters of the estimator. In
the case of supervised learning estimators, this method typically returns the
predicted labels or values computed by the model. Some unsupervised learning
estimators may however also implement that interface: for example, in clustering
estimators, \texttt{predict} returns the identifiers of the closest clusters for
the samples in \texttt{X}.

Along with the \texttt{predict} method, predictors may also implement methods
for quantifying the certainty of a prediction. In the case of estimators
implementing linear models, the \texttt{decision\_function} method can be used
to measure the distance of the samples from the discriminating hyperplane. Some
predictors also provide a \texttt{predict\_proba} method which returns
class probabilities for the input samples \texttt{X}.

Finally, predictors should also provide a \texttt{score} function to assess the
goodness of fit on some input data. In supervised learning estimators, this
method takes as inputs a dataset \texttt{X} and \texttt{y} and typically
computes the coefficient of determination between \texttt{y} and
\texttt{predict(X)} in the case of classification or the mean squared error in
the case of regression. Not however that, from an API point of view, the only
guideline is that the \texttt{score} method returns a numerical value such that
the higher the better. As such, some unsupervised learning estimators also
exposes a \texttt{score} function, computing for instance the likelihood of the
given data.

Continuing with the previous example, predictions on unseen data
\texttt{X\_test}, \texttt{y\_test} can therefore be obtained and evaluated using
the following snippet:
\begin{center}
\texttt{y\_hat = clf.predict(X\_test)}\\
\texttt{score = clf.score(X\_test, y\_test)}
\end{center}

\textbf{Transformers.} Since it is common to modify or filter data before
feeding it to some learning algorithm, some estimators in the library implement
a \textit{transformer} interface which defines a \texttt{transform} method
taking as input some dataset \texttt{X} and yielding as output a transformed
version of \texttt{X}\footnote{From an implementation point of view, it may
sometimes be more efficient to implement \texttt{fit} and \texttt{transform} in
a single method. In that case, transformers may expose an additional
\texttt{fit\_transform} method.}. In particular, all preprocessing algorithms
and feature selection routines are offered as transformers within the library.

In our example, if one wanted to transform the inputs \texttt{X} before
fitting the linear regression estimator, e.g., by standardizing the feature values,
one could thus simply write:
\begin{center}
\texttt{X = StandardScaler().fit(X).transform(X)}
\end{center}

@@
